
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{siunitx}
\usepackage{hyperref,graphicx,booktabs,dcolumn}
\usepackage{stata}
\usepackage[x11names]{xcolor}
\usepackage{natbib}
\usepackage{chngcntr}
\usepackage{pgfplotstable}
\usepackage{pdflscape}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[section]{placeins}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}

\newcommand{\specialcelr}[2][c]{%
  \begin{tabular}[#1]{@{}r@{}}#2\end{tabular}}

\newcommand{\thedate}{\today}

\counterwithin{figure}{section}
\counterwithin{table}{section}

\bibliographystyle{unsrt}
\renewcommand{\bibsection}{\section*{Publications}}

\begin{document}

\begin{titlepage}
    \begin{center}
        \Huge
        \textbf{CURRICULUM VITAE \\
JEDIDIAH INDIGO MORTON}
\rule{16cm}{2mm} \\
\Large
\thedate \\
       \vfill
    \end{center}
        \Large

\noindent
Email: \color{blue}
 \href{mailto:Jedidiah.Morton@Monash.edu}{Jedidiah.Morton@monash.edu} \\
\color{black}
Phone: \color{blue} 0403 487 378 \\
\color{black}
 \\
Research Fellow \\
Monash University, Melbourne, Australia. \\
381 Royal Parade, Parkville, Victoria, Australia, 3052. \\
 \\
Postdoctoral Researcher \\
Baker Heart and Diabetes Institute, Melbourne, Australia. \\
75 Commercial Road, Melbourne, Victoria, Australia, 3004. \\
\\
\end{titlepage}

\tableofcontents


\color{white}
\cite{DoodyAGG2024,
MacPE2024,
MortonDRCP2024,
TanCPT2024,
LivoriIJC2024,
LivoriEJPC2023,
MacCO2024,
FelekeDRCP2023,
LordPPT2023,
AbebeEHJ2023,
MortonPECA2023,
MortonAJKD2023,
DoodyAGG2023,
MacCirc2023,
DinaPE2023,
LloydDLOGIA2023,
MortonVIH2023,
TomicDRCP2023,
LazzDLOGIA2023,
QuigleyDRCP2022,
MacVIH2022,
MortonDLOGIA2023,
TomicDRCP2022,
TomicLDE2022,
MortonEJPC2023,
AdemiPE2022,
MortonDRCP2022,
MortonDM2022b,
MortonJECH2022,
OyunTAEM2022,
RuizDLOGIA2022,
MortonDC2022,
MortonJONS2022,
HastingsPE2022,
MortonDM2022a,
HardingNDT2022,
OyunSR2021,
MortonDC2021,
MortonDLOGIA2021,
MortonDC2020}
\color{black}

\pagebreak


\section*{Professional Appointments}
\addcontentsline{toc}{section}{Professional appointments}

\begin{tabular}{p{2cm}p{14cm}}
2023- & Baker Heart and Diabetes Institute. Postdoctoral researcher. \\
2022- & Monash University. Research fellow. \\
2021-2022 & Monash University. Teaching associate. \\
2019-2022 & Monash University. Monash University and Baker Heart and Diabetes Institute. PhD candidate. \\
2018-2019 & Monash University. University of Melbourne. Research assistant. \\
\end{tabular}

\section*{Other positions}
\addcontentsline{toc}{section}{Other positions}
\begin{tabular}{p{2cm}p{14cm}}
2023- & International Diabetes Federation, Diabetes Atlas Economic Impact of Diabetes Special Interest Group. Member. \\
2023- & Victorian Government, Department of Health, 
Safer Care Victoria Cardiovascular Learning Health Network Data Group. Member. \\
2022- & GLOBODIAB study. Principal analyst.  \\
2022 & Baker Heart and Diabetes Institute. Honorary appointment.  \\
\end{tabular}

\section*{Qualifications}
\addcontentsline{toc}{section}{Qualifications}
\begin{tabular}{p{2cm}p{14cm}}
2018 & Bachelor of Science (Honours), University of Melbourne. \\
2022 & Doctor of Philosophy, Monash University. \\
\end{tabular}

\section*{Scholarships and Awards}
\addcontentsline{toc}{section}{Scholarships and awards}
\begin{tabular}{p{2cm}p{14cm}}
2022 & Finalist – Victorian Premier's Awards for Health and Medical Research, Department of Health, Victorian Government. \\
2022 & Damien Jolly Award for Higher Degree by Research Thesis Excellence, Monash University. \\
2022 & Baker research prize for publication excellence, Baker Heart and Diabetes Institute. \\
2021 & Finalist – Baker best publication award, Baker Heart and Diabetes Institute. \\
2021 & Baker research prize for publication excellence, Baker Heart and Diabetes Institute. \\
2021 & School of Public Health and Preventive Medicine best HDR paper award, Monash University. \\
2020 & Finalist – Baker best publication award, Baker Heart and Diabetes Institute \\
2019-2022 & Monash Graduate Excellence Scholarship, Monash University. \\
2019-2022 & Australian Government Research Training Program Scholarship, Monash University. \\
2018 & John A. McKenzie / Selby Scientific Foundation Award, University of Melbourne. \\
2017 & Howitt Natural History Scholarship, University of Melbourne. \\
2016-2017 & Dean's Honours List, University of Melbourne. \\
\end{tabular}

\section*{Competitive grant funding}
\addcontentsline{toc}{section}{Competitive grant funding}
\begin{tabular}{p{2cm}p{14cm}}
2023 & 45 and Up Cardiovascular Research Grant, The Heart Foundation. \$120,000. \\
\end{tabular}



\clearpage
\addcontentsline{toc}{section}{Publications}
\bibliography{/home/jed/Documents/Library.bib}
\clearpage

\addcontentsline{toc}{section}{Textbook chapters}
\section*{Invited lectures}
\begin{enumerate}
\item Papadimos E, Morton JI, Harding JL, Barr E. 
A Life Course Approach to Diabetes. 
In Mishra G, Hardy R, Kuh D, A Life Course Approach to Women's Health (2nd edition). 
Oxford University Press.  
\end{enumerate}

\addcontentsline{toc}{section}{Invited lectures}
\section*{Invited lectures}
\begin{enumerate}
\item The Society of Hospital Pharmacists of Australia (SHPA) – Medicines Management 2023. "RCT or bust". November 2023.
\item Deakin University, Melbourne, Australia. "Inequality in type 2 diabetes in Australia". June 2023. 
\item Buloke Loddon Gannawarra Diabetes Online Forum, Victoria, Australia. "Up-to-date diabetes treatment? Depends on where you live." January 2022.  
\end{enumerate}

\addcontentsline{toc}{section}{Conference presentations}
\section*{Conference presentations}
\begin{enumerate}
\item Morton, JI, Marquina C, Lloyd M, Watts GF, Zoungas S, Liew D, Ademi Z. 
Lipid Lowering Strategies for Primary Prevention of Coronary Heart Disease in Australia: 
A Cost-effectiveness Analysis Using Mendelian Randomisation. 
Cardiac Society of Australia and New Zealand, August 2023.
\item Morton JI, Lazzarini PA, Polkinghorne KR, Carstensen B, Magliano DJ, Shaw JE. 
The Association between Age of Onset of Type 2 Diabetes and the Long-Term Risk for Major Diabetes-Related Complications. 
American Diabetes Association, June 2022. 
\item Morton JI, Marquina C, Shaw JE, Liew D, Ademi Z, Magliano DJ. 
Projecting the Incidence and Costs of Major Cardiorenal complications of 
Type 2 diabetes with Widespread GLP-1 RA and SGLT2i use. 
International Society for Pharmacoeconomics and Outcomes Research, May 2022.
\item Morton JI, Ilom{\"a}ki J, Wood SJ, Magliano DJ, Shaw JE. 
Trends in Rehospitalisation Rates for Myocardial Infarction, Heart Failure, and Stroke in People with
and without Diabetes in Australia from 2012-2018. American Diabetes Association, June 2021.
\item Morton JI, McDonald SP, Salim A, Liew D, Shaw JE, Magliano DJ. 
Projecting the Future Incidence of Type 2 Diabetes-Related End-Stage Kidney Disease: 
A Comparison between Diabetes Prevention and Treatment. Australasian Diabetes Congress 2020.
\item Morton JI, Liew D, McDonald SP, Shaw JE, Magliano DJ. 
The Association of Age of Onset of Type 2 Diabetes with Long-Term Risk of End Stage Kidney Disease: 
A National Registry Study. American Diabetes Association, June 2020.  
\end{enumerate}

\addcontentsline{toc}{section}{Invited articles}
\section*{Invited lectures}
\begin{enumerate}
\item Morton JI. Sweet Saviour: Increasing availability of a new diabetes medication could prevent many people with 
type 2 diabetes developing kidney failure. Diabetic Living (readership: 245,000; circulation: 56,739), 2021. 
\end{enumerate}


\addcontentsline{toc}{section}{Supervision}
\section*{Supervision}
\begin{enumerate}
\item Della Wang. Doctor of Philosophy. Monash University. Associate supervisor. 
\item Sheridan Rodda. Doctor of Philosophy. Monash University. Associate supervisor. 
\item Tamrat Befekadu Abebe. Doctor of Philosophy. Monash University. Associate supervisor. 
\item Adam Livori. Doctor of Philosophy. Monash University. Associate supervisor. 
\item George Tan. Doctor of Philosophy. Monash University. Associate supervisor. 
\item Hannah Doody. Masters of Clinical Pharmacy. Monash University. Primary supervisor. 
\item Anthony Horton. Masters of Public Health. Monash University. Primary supervisor.
\end{enumerate}

\addcontentsline{toc}{section}{Teaching}
\section*{Supervision}
\begin{enumerate}
\item Monash University. BMS4200: Biostatistics for Biomedicine (Honours). Teaching associate.
\item Monash University. PGC5101: Evidence based practice (Master of Clinical Pharmacy). Teaching associate and interim unit coordinator.
\item Monash University. PHR2012: Professional Practice IV (Bachelor of Pharmacy). Teaching associate.
\item Monash University. MPS5304: Regulatory science and monitoring medicine use (Master of Clinical Pharmacy). Guest lecturer.
\item Baker Heart and Diabetes Institute. Multistate models: Occurrence rates, cumulative risks, 
competing risks, state probabilities with multiple states and time scales using R and Epi::Lexis, by Bendix Carstensen. Teaching assistant.
\end{enumerate}

\addcontentsline{toc}{section}{Peer review}
\section*{Peer review}
I have reviewed manuscripts for the following journals:
\begin{itemize}
\item The Lancet Diabetes and Endocrinology 
\item European Heart Journal 
\item Diabetes Care 
\item Medical Journal of Australia 
\item Diabetologia 
\item American Journal of Kidney Diseases 
\item The Lancet Regional Health – Western Pacific 
\item Cardiovascular Diabetology 
\item Diabetes Research and Clinical Practice 
\item Diabetes \& Metabolism 
\item Diabetic Medicine 
\item Diabetes, Obesity and Metabolism 
\item Value in Health 
\item PharmacoEconomics 
\item BMJ Open 
\item Frontiers in Endocrinology 
\item Scientific Reports 
\item European Journal of Clinical Investigation 
\item Annals of Medicine 
\item Journal of Epidemiology and Community Health 
\item Journal of Clinical Lipidology 
\item BMC Nephrology 
\item BMC Public Health 
\item BMC Health Services Research 
\item Current Medical Research  \& Opinion 
\item Health Economics Review 
\item Journal of Pharmacy Practice and Research 
\end{itemize}


\end{document}

